Occurrence and transmission potential of asymptomatic and pre-symptomatic SARS-CoV-2 infections: a living systematic review and meta-analysis

### 2021-11-04 Manuscript_draft.Rmd
Update Manuscript_draft.Rmd

dfQ3b=data.frame(label=paste0("   ",asymptomaticQ2_2$author_1),
                 Q3set=NA,
                 p = asymptomaticQ2_2$q3_pa_m, 
                 l = asymptomaticQ2_2$q3_pa_l,
                 h = asymptomaticQ2_2$q3_pa_u,
                 setting="Asymptomatic",stringsAsFactors = FALSE)

dfQ3b[dfQ3b==9999]<-NA
dfQ3b=dfQ3b[!is.na(dfQ3b$p),]

>>>>

dfQ3b=data.frame(label=paste0("   ",asymptomaticQ2_2$author_1),
                 Q3set=asymptomaticQ2_2$q3_setting,
                 p = asymptomaticQ2_2$q3_pa_m, 
                 l = asymptomaticQ2_2$q3_pa_l,
                 h = asymptomaticQ2_2$q3_pa_u,
                 setting="Asymptomatic",stringsAsFactors = FALSE)

dfQ3b[dfQ3b==9999]<-NA
dfQ3b=dfQ3b[!is.na(dfQ3b$p),]
#dfQ3b[5,3:5] <- gsub("%", "",dfQ3b[5,3:5])
dfQ3b <- rbind(dfQ3b,dfQ3b[2,])

dfQ3b[2,] <- gsub(";.*","",dfQ3b[2,])
dfQ3b[4,] <- gsub(".*;","",dfQ3b[4,])
dfQ3b[dfQ3b==9999]<-NA
dfQ3b[dfQ3b=="NA"]<-NA
dfQ3b$Q3set[3] <-NA

dfQ3b$label=ifelse(dfQ3b$label=="   Moghadas SM",
                   paste0(dfQ3b$label, " ", ifelse(!is.na(dfQ3b$Q3set),paste0("[",dfQ3b$Q3set,"]"),"")),dfQ3b$label)

dfQ3b$Q3set <- NA
